MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-13 docs/paper/out/paper.tex
add specific versions for libs with link to releases -- paper
WARNING: some of them do not exist yet, but they should be the ones
that we will use.

@laughedelic please review.

@@

@@

\subsection{Type-safe DSLs for BLAST and
FLASH}\label{type-safe-dsls-for-blast-and-flash}

We developed our own type-safe DSLs (Domain Specific Language) for
\href{https://github.com/ohnosequences/flash}{FLASH} and
\href{https://github.com/ohnosequences/blast}{BLAST} expressions and
their execution.

\subsubsection{BLAST DSL}\label{blast-dsl}

@@

\subsubsection{FLASH DSL}\label{flash-dsl}

In the same spirit as for BLAST,

@@

>>>>

MG7 uses
\href{https://github.com/statika/statika/releases/tag/v0.2.0}{ohnosequences/statika
2.0.0}.

@@

MG7 uses
\href{https://github.com/ohnosequences/datasets/releases/tag/v0.2.0}{ohnosequences/datasets
0.2.0}.

@@

MG7 uses
\href{https://github.com/ohnosequences/loquat/releases/tag/v?.?.?}{ohnosequences/loquat
?.?.?}.

\subsection{Type-safe EDSLs for BLAST and
FLASH}\label{type-safe-edsls-for-blast-and-flash}

We developed our own Scala-based type-safe EDSLs (Embedded Domain
Specific Language) for
\href{https://github.com/ohnosequences/flash}{FLASH} and
\href{https://github.com/ohnosequences/blast}{BLAST} expressions and
their execution.

\subsubsection{BLAST EDSL}\label{blast-edsl}

@@

MG7 uses
\href{https://github.com/ohnosequences/blast/releases/tag/v0.2.0}{ohnosequences/blast
0.2.0}.

\subsubsection{FLASH EDSL}\label{flash-edsl}

In the same spirit as for BLAST, we implemented a type-safe EDSL for
FLASH expressions and their execution, sporting features equivalent to
those outlined for the BLAST EDSL.

MG7 uses
\href{https://github.com/ohnosequences/flash/releases/tag/v0.1.0}{ohnosequences/flash
0.1.0}.

@@

MG7 uses
\href{https://github.com/bio4j/bio4j/releases/tag/v0.12.0-RC3}{bio4j/bio4j
0.12.0-RC3} and
\href{https://github.com/bio4j/bio4j-titan/releases/tag/v0.4.0-RC2}{bio4j/bio4j-titan
0.4.0-RC2}.
